On the marginal value of swimming in woodland caribou

### 2021-05-25 paper/manuscript.Rmd
conclusion

From our natural history observation and proximal movement data on caribou swimming, characteristics
of destination islands, and residency on the islands, we have presented some evidence for the marginal
value of resources that may serve as for evidence of forage limitation. Further investigation into the
nuance of forage profitability, local density, and the role of both social and spatial cognition is
needed. Here, we have proposed a thought exercise that integrates the marginal value theorem with a
novel natural history observation to explain swimming behavior for terrestrial animals and opens the
door for future studies of caribou in our system and other island archipelagos inhabited by caribou.

>>>>

From our natural history observations and proximal movement data on caribou swimming, characteristics of destination islands, and residency on the islands, we have presented some evidence for the marginal value of resources that may serve as evidence of forage limitation for caribou swimming between islands. Further investigation into the nuance of forage profitability, local density, and the role of both social and spatial cognition is needed. Here, we have proposed a thought exercise that integrates the marginal value theorem with novel natural history observations to explain swimming behavior for terrestrial animals and opens the door for future studies of caribou in our system and other island archipelagos inhabited by caribou.
